Applying a clever histogram method to the square-well liquid

### 2014-05-04 papers/square-well-liquid/histogram-paper.tex
truncate walker optimization weight histogram at max entropy point, so as to not waste time at high energy states. also fixed problem with histogram-paper not finding a figure Tested on quipu. Took 0:23.34.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N200-E.pdf}
  \caption{A histogram plot demonstrating the difficulty of using
    canonical Monte Carlo to simulate a system.  A simulation at a
    give temperature only provides information fo a small number of
    energy states.\label{fig:histograms}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N200-dos.pdf}
  \caption{A density of states plot demonstrating the difficulty of using
    canonical Monte Carlo to simulate a system.  A simulation at a
    give temperature only provides information fo a small number of
    energy states.\label{fig:histograms}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N200-u.pdf}
  \caption{Specific internal energy.\label{fig:u}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N200-hc.pdf}
  \caption{Specific heat capacity.\label{fig:hc}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N200-rd.pdf}
  \caption{Radial distribution function.\label{fig:rdf}}
\end{figure}

>>>>

\graphicspath{ {figs/} }

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{periodic-ww130-ff30-N200-E.pdf}
  \caption{A histogram plot demonstrating the difficulty of using
    canonical Monte Carlo to simulate a system.  A simulation at a
    give temperature only provides information fo a small number of
    energy states.\label{fig:histograms}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{periodic-ww130-ff30-N200-dos.pdf}
  \caption{A density of states plot demonstrating the difficulty of using
    canonical Monte Carlo to simulate a system.  A simulation at a
    give temperature only provides information fo a small number of
    energy states.\label{fig:dos}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{periodic-ww130-ff30-N200-u.pdf}
  \caption{Specific internal energy.\label{fig:u}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{periodic-ww130-ff30-N200-hc.pdf}
  \caption{Specific heat capacity.\label{fig:hc}}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{periodic-ww130-ff30-N200-rdf.pdf}
  \caption{Radial distribution function.\label{fig:rdf}}
\end{figure}
